---
title: "My Fancy PResentation"
author: "Ken Wade"
date: "November 8, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slide
Some content

## My Title
- Bullet one
- Bullet two
1. item a
2. item b

Plain Text
*italicized text*
**Bold Text**
`for (i %in% 1:10)`

## Another New Slide

```{r, echo=FALSE, fig.align='center', fig.cap='My AWESOME figure'}
plot(mtcars$wt, mtcars$mpg, xlab="Weight", ylab="MPG")
```



***
A Slide without a title



## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

